### 2020-03-07 short.body.tex
updated to 18%

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
The solid, white lines represent the contours.
The solid, black lines represent the example scenario that assumes $p = 0.35$ and $\mathcal R_a = 0.5 \mathcal R_s$.
The solid, black circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
\label{fig.relevance}}
\end{center}
\end{figure*}

@@

As an example, we assume that 35\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
The intrinsic proportion of asymptomatic transmission $z$ is 0.27, but asymptomatic cases can account for anywhere between 17\% and 35\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
Likewise, the basic reproduction number ranges between 2.2 and 2.8 (Figure~\ref{fig.relevance}B).
Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; black circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.

>>>>

\begin{figure*}[b!]
\begin{center}
\includegraphics[width=0.4\textwidth]{figheatmap.pdf}
\mbox{\hspace{0.05\textwidth}}
\includegraphics[width=0.4\textwidth]{figheatmap_R0.pdf}
\caption{Effects of intrinsic proportion of asymptomatic transmission on the relevance of asymptomatic transmission and basic reproduction number, given variation in
the mean generation interval of asymptomatic cases. 
(A) Long/short generation intervals of asymptomatic cases decrease/increase the relevance of asymptomatic cases, $q$.
(B) Long/short generation intervals of asymptomatic cases increase/decrease the basic reproduction number ${\cal{R}}_0$.
We vary $G_a/G_s$ while assuming $1/r=7$ days, $\bar G_s=8$ days, and $\kappa_s=\kappa_a=0.5$.
The solid, white lines represent the contours.
The solid, red lines represent the example scenario that assumes $p = 0.18$ and $\mathcal R_a = 0.5 \mathcal R_s$.
The solid, red circles represent the baseline value that does not explicitly account for asymptomatic transmission; depending on whether $G_a$ is smaller or bigger than $G_s$, the baseline value over- or under-estimates the true $\mathcal R_0$.
\label{fig.relevance}}
\end{center}
\end{figure*}

@@

As an example, we assume that 18\% of the newly infected cases are asymptomatic \citep{mizumoto_2020} and that the asymptomatic cases are as half as infectious as the symptomatic ones (i.e., $\mathcal R_a = 0.5 \mathcal R_s$).
The intrinsic proportion of asymptomatic transmission $z$ is 0.11, whereas asymptomatic cases can account for anywhere between 6\% and 16\% of infection during the exponential growth phase across the range of mean asymptomatic generation interval we explore (Figure~\ref{fig.relevance}A).
Likewise, the basic reproduction number ranges between 2.3 and 2.6 (Figure~\ref{fig.relevance}B).
Therefore, when ${\cal{R}}_0$ is estimated without explicitly accounting for asymptomatic spread ($\mathcal R_0=2.5$; red circle in Figure~\ref{fig.relevance}B), it can be over- or under- estimated depending on the relative duration of infection between symptomatic and asymptomatic individuals.
